Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
Small corrections
Figuring out how to report stats.

We recruited 40 participants for the study.
One did not complete the study and 5 participants had to be removed because they said they cheated during the study.
We used the data from the remaining 34 participants for our analysis.

@@

\todo{What are the means and variance of different variables?}

@@

\subsubsection{RQ1: Is there a bias?}

>>>>

We recruited 40 participants for the study.
One did not complete the study and 5 participants had to be removed because they said they cheated during the study.
They said they wrote down the data in the visualizations, despite the instructions asking them them not to.
We used the data from the remaining 34 participants for our analysis.

@@

\todo{What are the means and variance of different variables?}%DAE: what are you thinking of here? Like for the bias, or for confidence?

@@

\subsubsection{RQ1: Does incorrect approximate data bias responses about correct data?}

Our results suggest that viewing incorrect approximate data biases participant responses about correct data for certain types of questions.
For question type 1, how many, the expected bias had no impact on participant response $(t)$.
